An Automatic Verification Framework for Software Configurations

### 2016-05-07 OSDI/learner-ranges.tex
add intuition for ranges

>>>>

The intuition for this test is that if the user has input a value that falls outside of an 
interval containing values that are considered "normal" over the entire data set, 
that value will probably cause an error, in particular for performance. We cannot know for sure
if this value will cause an issue. For instance, a user might have a machine with 
particularly high-end hardware, in which case a value beyond the upper Hampel threshold may be appropriate.
